Temporality is Important for Networks of Hospital Patient Transfers

### 2024-11-25 reports/report.qmd
Add newer report ideas

sns.set_theme(style='ticks')
sns.set_context('paper')
# plt.style.use('ggplot')
```

@@

```{dot}
//| fig-width: 30%
digraph G {
    S₀ -> S₁ [ label="λ₀" ]
}
```

```{dot}
//| fig-width: 50%
digraph G {
    S₀ -> S₁ [ label="λ₀p" ]
    S₀ -> S₂ [ label="λ₀(1-p)" ]
    S₂ -> S₁ [ label="λ₂" ]
}
```

@@

In the model without indirect transfer, we can compute the expected hitting time $k_{1}$ from $S_0$ to $S_1$ as

@@

i.e. the hitting time is increased by $\frac{1-p}{\lambda_2}$.

>>>>

sns.set_theme(style='ticks')
sns.set_context('paper')
plt.style.use('tableau-colorblind10')
```

@@

```{dot}
//| fig-width: 30%
digraph G {
    A -> B [ label="λ₀" ]
}
```

```{dot}
//| fig-width: 50%
digraph G {
    A -> B [ label="λ†p" ]
    A -> H [ label="λ†(1-p)" ]
    H -> B [ label="λₕ" ]
}
```

@@

::: {#new-eq}

Let us denote the (empirical) distribution of return times as $f(T)$, where $T$ is the return time.
Then for a naive model, we have that the hazard of moving between two hospitals is approximately
$\lambda_0 = (\mathbb{E}(A \to B))^{-1} = (\int_0^{\infty} f(T) T dT)^{-1}$

For the refined model, we have instead two processes

$A \to B$ and $A \to H \to B$,

where

$\mathbb{E}(T_{A\to B}) = \int_0^{\Omega} f(T) T dT$

and

$\mathbb{E}(T_{A\to H\to B}) = \int_\Omega^{\infty} f(T) T dT$

We could simulate with some rate $\lambda_\dagger$ so that

$\lambda_d = \mathbb{E}(T_{A\to B})^{-1} = \lambda_\dagger \times p$

and

$\lambda_x = \lambda_\dagger \times (1-p)$ (indirect)

AND

$p = \int_0^{\Omega} f(T) dT$ is the proportion of individuals that take the direct path.

Thus we can recover that $\lambda_\dagger = \left(\int_0^{\Omega} f(T) T dT\right)^{-1} \int_0^{\infty} f(T) dT$.

And if we require that

$(\lambda_x)^{-1} + (\lambda_h)^{-1} = \int_\Omega^{\infty} f(T) T dT$

and so

$$
\begin{aligned}
(\lambda_h)^{-1} &= \left[\int_\Omega^{\infty} f(T) T dT \right] - (\lambda_\dagger (1-p))^{-1}\\
&= \left[\int_\Omega^{\infty} f(T) T dT \right] - \left[\left[\int_0^{\Omega} f(T) T dT \right]^{-1} {\int_\Omega^{\infty} f(T) dT} \right]^{-1}\\
&= \left[\int_\Omega^{\infty} f(T) T dT \right] - \left[\int_0^{\Omega} f(T) T dT \frac{1}{\int_\Omega^\infty f(T) dT}\right]
\end{aligned}
$$

We also need that $(\lambda_\dagger (1-p))^{-1} < \int_\Omega^{\infty} f(T) T dT$ (is this always possible?)

If $T \sim Exp(\lambda)$, then $f(T) = \lambda \exp(-\lambda T)$ and $F(T) = 1 - \exp(-\lambda T)$.
We can also find that $\int_a^b f(T) T dT = \left[ -(T + \lambda^{-1}) \exp(-\lambda T) \right]^b_a$, so that

$\int_0^\Omega f(T) T dT = -(\Omega + \lambda^{-1}) \exp(-\lambda \Omega) + (0 + \lambda^{-1}) \exp(-\lambda 0) = \lambda^{-1} (1- \exp(-\lambda \Omega)) - \Omega \exp(-\lambda \Omega)$

and

$\int_\Omega^\infty f(T) T dT = (\Omega \lambda^{-1}) \exp(-\lambda \Omega)$

so that

$(\lambda_\dagger (1-p))^{-1} = [\lambda^{-1} (1- \exp(-\lambda \Omega)) - \Omega \exp(-\lambda \Omega)]  \frac{1}{\exp(-\lambda \Omega)}$

We can then say that 
:::

<!-- In the model without indirect transfer, we can compute the expected hitting time $k_{1}$ from $S_0$ to $S_1$ as

@@

i.e. the hitting time is increased by $\frac{1-p}{\lambda_2}$. -->
